Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-06 tese2/09_related_work_signaling.tex
[FIX] reference to stroph.js

  \ac{XMPP} was initially developed for instant messaging and presence (Jabber\footnote{\url{http://jabber.org/}(accessed June 1, 2015).}). It is nowadays an open technology for standardized, decentralized, secure and extensible real-time communications. 
  \ac{XMPP} messages are \ac{XML} based, which is attractive for applications that need structured messages and rich hypermedia. Another advantage of \ac{XMPP} is the addition of extensions, for example \emph{XEP-0096}\cite{xep0096}, which adds file transfer capabilities between two entities, and \emph{XEP-0045}\cite{xep0045}, which enables multi-user chat.
  \ac{XMPP}'s bi-directional communication over \ac{HTTP} is achieved through \ac{BOSH} \cite{xep0206}.
  %RP falta um `` bi-directional communication OVER HTTP is achieved through''?
  %RP BOSH já foi explicado antes pelo que não vale a pena voltar a falar em long-pooling
  This kind of communication is also possible through WebSockets \cite{rfc7395}.
  Today, multiple \ac{XMPP} server implementations exists, such as: \emph{ejabberd}\footnote{\url{http://jabberd.im/}(accessed June 1, 2015).}, \emph{Metronome}\footnote{\url{http://lightwitch.org/metronome}(accessed June 1, 2015).}, \emph{Openfire}\footnote{\url{http://igniterealtime.org/projects/openfire/}(accessed June 1, 2015).} and \emph{Prosody}\footnote{\url{http://prosody.im/}(accessed June 1, 2015).}. \emph{Ejabberd} is the server that implements more \ac{RFC} specifications and \ac{XEP}s\footnote{\url{http://en.wikipedia.org/wiki/Comparison_of_XMPP_server_software}(accessed June 1, 2015).}.
  %RP fazes muitos paragrafos. Um paragrafo por tecnologia é normalmente suficiente se não forem muito grandes.

@@

    An important aspect of this model is the ability to define a user as a set of attributes that can change dinamically in order to fit the \ac{IM} application's needs.

    The connection to the \ac{XMPP} server can be done through the same web server as the user is connected, but this web server would handle a lot of connections and that would have a great impact on the overall system performance.

    Typically a web application consists in multiple web pages which are navigated by users. Each time a webpage is accessed, either from a new context or a transition from a previous page, its context is cleared except for local storage and cookies. The javascript context is cleared, including the \ac{XMPP} connections performed by \emph{strophe.js}. As such, an automatic mechanism is required for avoiding the implicit user reauthentication.
    One solution for reauthentication can be achieved by storing the user's JabberID and password on local storage and everytime a page is accessed the authentication is performed without the users knowledge. Clearly this solution represents security flaws as the local storage can be easily accessed locally or by performing a cross site scripting attack to reveal all the local storage. The same problem arises if the credentials are stored on cookies.
    %RP tinhas este comentário (HOW? explain!)
    %RP o strophe.js caiu aqui da paraquedas! Explicar o que é

    An alternative solution is known as Session Attachment \footnote{\url{https://metajack.im/2008/10/03/getting-attached-to-strophe/}}, which requires that a \textit{session identifier}(SID) together with a \textit{initial request identifier (RID)} be passed to strophe.js in order to re-connect to the same stream on \ac{XMPP} server. Either SID and RID are unpredictable and, particularly, \textit{RID} changes on every request making it worthless if a user mantains more than one tab opened, for example for multiple conversations at the same time.
    %RP either ou both?
    %RP verifica se não alterei o sentido da frase

    Another alternative would be the development of our solution in a single web page, which would increse drastically the complexity of our web application.

    We know that an \ac{XMPP} based application could simplify our work just by using functionalities that \ac{XMPP} already implemment, but  we don't need all of them. In fact, we just need a subset of \ac{XMPP} features, namely a simple way to register users, access and edit user's information, create chat rooms, send messages and access to presence information.
}

>>>>

  \ac{XMPP} was initially developed for instant messaging and presence (Jabber\footnote{\url{http://jabber.org/}(accessed June 1, 2015).}). It is nowadays an open technology for standardized, decentralized, secure and extensible real-time communications. 
  \ac{XMPP} messages are \ac{XML} based, which is attractive for applications that need structured messages and rich hypermedia. Another advantage of \ac{XMPP} is the addition of extensions, for example \emph{XEP-0096}\cite{xep0096}, which adds file transfer capabilities between two entities, and \emph{XEP-0045}\cite{xep0045}, which enables multi-user chat.
  \ac{XMPP}'s bi-directional communication over \ac{HTTP} is achieved through \ac{BOSH} \cite{xep0206}.
  This kind of communication is also possible through WebSockets \cite{rfc7395}.
  Today, multiple \ac{XMPP} server implementations exists, such as: \emph{ejabberd}\footnote{\url{http://jabberd.im/}(accessed June 1, 2015).}, \emph{Metronome}\footnote{\url{http://lightwitch.org/metronome}(accessed June 1, 2015).}, \emph{Openfire}\footnote{\url{http://igniterealtime.org/projects/openfire/}(accessed June 1, 2015).} and \emph{Prosody}\footnote{\url{http://prosody.im/}(accessed June 1, 2015).}. \emph{Ejabberd} is the server that implements more \ac{RFC} specifications and \ac{XEP}s\footnote{\url{http://en.wikipedia.org/wiki/Comparison_of_XMPP_server_software}(accessed June 1, 2015).}.
  %RP fazes muitos paragrafos. Um paragrafo por tecnologia é normalmente suficiente se não forem muito grandes.

@@

    An important aspect of this model is the ability to define a user as a set of attributes that can change dynamically in order to fit the \ac{IM} application's needs.

    The connection to the \ac{XMPP} server can be done through the same web server as the user is connected, but this web server would handle a lot of connections and that would have a great impact on the overall system performance. On the other hand, users can directly connect directly to \ac{XMPP} servers from web applications using the \emph{JavaScript} library \emph{strophe.js} \footnote{\url{http://strophe.im/strophejs/} (accessed May 6, 2016).}

    Typically a web application consists in multiple web pages which are navigated by users. Each time a web page is accessed, either from a new context or a transition from a previous page, its context is cleared except for local storage and cookies. The \emph{JavaScript} context is cleared, including the \ac{XMPP} connections performed by \emph{strophe.js}. As such, an automatic mechanism is required for avoiding the implicit user reauthentication.
    One solution for reauthentication can be achieved by storing the user's JabberID and password on local storage and every time a page is accessed the authentication is performed without the users knowledge. Clearly this solution represents security flaws as the local storage can be easily accessed locally or by performing a cross site scripting attack to reveal all the local storage. The same problem arises if the credentials are stored on cookies.
    %RP tinhas este comentário (HOW? explain!)
    %RP o strophe.js caiu aqui da paraquedas! Explicar o que é

    An alternative solution is known as Session Attachment \footnote{\url{https://metajack.im/2008/10/03/getting-attached-to-strophe/} (accessed May 6, 2016).}, which requires that a \textit{session identifier}(SID) together with a \textit{initial request identifier (RID)} be passed to \emph{strophe.js} in order to re-connect to the same stream on \ac{XMPP} server. Either SID and RID are unpredictable and, particularly, \textit{RID} changes on every request making it worthless if a user maintains more than one tab opened, for example for multiple conversations at the same time.
    %RP either ou both?
    %RP verifica se não alterei o sentido da frase

    Another alternative would be the development of our solution in a single web page, which would increase drastically the complexity of our web application.

    We know that an \ac{XMPP} based application could simplify our work just by using functionalities that \ac{XMPP} already implement, but  we don't need all of them. In fact, we just need a subset of \ac{XMPP} features, namely a simple way to register users, access and edit user's information, create chat rooms, send messages and access to presence information.
}
